---
title: "Degrowth critique"
author: "Ivan Savin"
date: "25/04/2023"
output: word_document

---

<style type="text/css">
body, td {
   font-size: 20px;
}
code.r{ / Code block /
    font-size: 6px;
}
</style>

```{r echo=FALSE}
rm(list=ls())
setwd("E:/Projects/2_Working Papers/Degrowth critique/Depository")
#install.packages(c("magrittr", "data.table", 'dplyr', 'ggplot2', 'cluster'))
sapply(c("magrittr", "data.table", 'plyr','dplyr', 'ggplot2', 'cluster','knitr', 'dendextend','pkgbuild','devtools','R.methodsS3','stm','ngram','matrixStats','corrplot','ggpubr','wordcloud','readxl','tm','igraph'), require, character.only = T)
# library(doParallel) 
# cl <- makeCluster(6, type='PSOCK')
# registerDoParallel(cl)

knitr::opts_chunk$set(fig.width=10, fig.height=10,dpi=300) #10 15

#data<-read_xlsx("startups_full_lang_NEW.xlsm")
#data<-read.csv('EIST_ Abstract & Keyword for published papers_v4.csv', header=T, sep=',')
data <- fread('data_degrowth_sept2023.csv') 
data<-data[1:594,]
data$`Empirical.Model`<-as.numeric(data$`Empirical.Model`)

data<-data[-which(data$include==0 | is.na(data$include)),]
names(data)[61]<-"Pub.Type"
names(data)[23]<-"citations"
data<-as.data.frame(data)
for (i in c(8:14,20)){
  data[,i]<-as.numeric(data[,i])
}
data$citations[which(is.na(data$citations))]<-0
data$Abstract[which(data$Abstract=="[No abstract available]")]<-NA

summary(data)
#head(data)
table(data$Pub.Type)
table(data$Year)
plot(table(data$Pub.Type),ylab="Frequency")


degrowth_count<-matrix(0,2,17)
thmodel_count<-matrix(0,2,17)
empmodel_count<-matrix(0,2,17)
qualdata_count<-matrix(0,2,17)
quantdata_count<-matrix(0,2,17)
j<-1
for (i in (2007:2023)){
  degrowth_count[1,j]<-i-.5
  degrowth_count[2,j]<-sum(data$degrowth[which(data$Year==i)])
  empmodel_count[1,j]<-i-.5
empmodel_count[2,j]<-sum(data$`Empirical.Model`[which(data$Year==i)])/sum(data$Year==i)*100
   thmodel_count[1,j]<-i-.5
thmodel_count[2,j]<-sum(data$`Theoretical.Model`[which(data$Year==i)])/sum(data$Year==i)*100
    qualdata_count[1,j]<-i-.5
qualdata_count[2,j]<-sum(data$`Qualitative.Data`[which(data$Year==i)])/sum(data$Year==i)*100
    quantdata_count[1,j]<-i-.5
quantdata_count[2,j]<-sum(data$`Quantitative.Data`[which(data$Year==i)])/sum(data$Year==i)*100
  j<-j+1
}

par(mfrow = c(2, 1), mar = c(5, 4, 1, 1) + 0.3)              # Additional space for second y-axis

# l <- list(data$Year,data$Year[data$degrowth==1])
# multhist(l, col=c('grey','red'),breaks=c(2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023), main="",ylab="Number of studies", xaxt="n", xlab="")
# axis(1, labels=c(2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023),las=2)
# legend("topleft", legend=c("All studies","Studies with 'degrowth' in title"),
#        col=c("grey","red"), lty=1, cex=0.6, horiz=TRUE)


hist(data$Year, breaks=c(2006,2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023), main="",ylab="Number of studies", xaxt="n", xlab="")
axis(1, at=c(2006.5,2007.5,2008.5,2009.5,2010.5,2011.5,2012.5,2013.5,2014.5,2015.5,2016.5,2017.5,2018.5,2019.5,2020.5,2021.5,2022.5), labels=c(2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023),las=2)

lines(x = degrowth_count[1,],y=degrowth_count[2,], col = "red")

legend("topleft", legend=c("Studies with 'degrowth' in title"),
       col=c("red"), lty=1, cex=0.8, horiz=TRUE)

plot(x = empmodel_count[1,],y=empmodel_count[2,], col = "blue",pch=0, xaxt="n", xlab="", ylab = "Percent",ylim=c(0,50))
lines(x = empmodel_count[1,],y=empmodel_count[2,], col = "blue")
axis(1, at=c(2006.5,2007.5,2008.5,2009.5,2010.5,2011.5,2012.5,2013.5,2014.5,2015.5,2016.5,2017.5,2018.5,2019.5,2020.5,2021.5,2022.5), labels=c(2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023),las=2) 
par(new = TRUE)

plot(x = empmodel_count[1,],y=thmodel_count[2,], col = "cyan",pch=0, xaxt="n", xlab="", ylab = "Percent",ylim=c(0,50))
lines(x = empmodel_count[1,],y=empmodel_count[2,], col = "cyan")
axis(1, at=c(2006.5,2007.5,2008.5,2009.5,2010.5,2011.5,2012.5,2013.5,2014.5,2015.5,2016.5,2017.5,2018.5,2019.5,2020.5,2021.5,2022.5), labels=c(2007,2008,2009,2010,2011,2012,2013,2014,2015,2016,2017,2018,2019,2020,2021,2022,2023),las=2) 
par(new = TRUE) 

plot(x = empmodel_count[1,],y=qualdata_count[2,], col = "orange",pch=1, axes = FALSE, xlab = "", ylab = "",ylim=c(0,50))
lines(x = qualdata_count[1,],y=qualdata_count[2,], col = "orange")
par(new = TRUE) 
plot(x = empmodel_count[1,],y=quantdata_count[2,], col = "magenta",pch=2, axes = FALSE, xlab = "", ylab = "",ylim=c(0,50))
lines(x = empmodel_count[1,],y=quantdata_count[2,], col = "magenta")
par(new = TRUE) 
legend("topleft", legend=c("Empirical \n model", "Theoretical \n model","Quantitative \n data","Qualitative \n data"),
       col=c("blue","cyan","magenta","orange"), lty=1, pch=0:2,cex=0.8, horiz=TRUE)

sort(table(data$`Source.title`), desreasing=TRUE)

# 
# sum(is.na(data$Abstract)) #number of papers with no abstract
# table(data$Pub.Type[which(is.na(data$Abstract))]) #most conference papers and editorials do not have an abstract


#lets exclude editorials, conference papers, reviews , erratum/retracted, and letters/notes from further analysis (also because they have many missing abstracts)
#data_clean<-data[-which(data$Pub.Type %in% c("Editorial","Conference paper", "Review", "Erratum", "Retracted","Letter","Note")),]
# data_clean<-data[-which(data$Dochead %in% c("Book review","Editorial","Analysis","Comments & Views","News","Policy brief","Survey","Viewpoint")),]
#lets delete papers without abstracts available
#data_clean<-data[-which(is.na(data$Abstract)),]
#data_clean<-data[-which(is.na(data$Accepted.DateM)),]
data_clean<-data

data_clean$TitleAbstract<-paste(data_clean$Title,data_clean$Abstract,data_clean$`Indexed Keywords`,data_clean$`Author Keywords`)
#Average length of response on economic growth is 1.94 words
data_clean$length_txt<-matrix(0,length(data_clean$TitleAbstract),1)

data_clean$length_txt<-sapply(1:length(data_clean$Abstract), function(x) wordcount(data_clean$TitleAbstract[x]))
par(mfrow = c(1, 1))
hist(data_clean$length_txt,breaks=100, main="Length of abstracts ",xlab="# of words")
summary(data_clean$length_txt)


data_clean$length_title<-matrix(0,length(data_clean$TitleAbstract),1)
data_clean$length_title<-sapply(1:length(data_clean$Title), function(x) wordcount(data_clean$Title[x]))

data_clean$citationspy<-matrix(0,length(data_clean$TitleAbstract),1)
data_clean$yearssincepub<-matrix(0,length(data_clean$TitleAbstract),1)
data_clean$yearssincepub<-sapply(1:length(data_clean$Year), function(x) max(1,2023-data_clean$Year[x]))
data_clean$citationspy<-data$citations/data_clean$yearssincepub
  
par(mfrow = c(1, 3))
hist(data_clean$length_title,breaks=100, main="Length of title ",xlab="# of words")
summary(data_clean$length_title)
#data_clean$citedby_count[which(is.na(data_lemmatized$citations))]<-0
hist(data_clean$citations,breaks=100, main="Number of citations",xlab="")
summary(data_clean$citations)
hist(data_clean$citationspy,breaks=100, main="Number of citations",xlab="")
summary(data_clean$citationspy)
# data_clean$TitleAbstract <- gsub("[[:punct:]]", " ", data_clean$TitleAbstract)  # replace punctuation with space
# 
# library("writexl")
# con<-file('data_language',encoding="UTF-8")
# write_xlsx(data_clean,"data_clean2.xlsx")
# write.csv(data_clean,"data_clean3.csv",fileEncoding = "ISO-8859-1")
#write.table(data_clean,file="data_clean4.csv",sep=",",dec = " ",fileEncoding = "ISO-8859-1")


par(mfrow = c(1, 2))
hist(data_clean$Year,breaks=53, main="",xlab="year of publication")
hist(data_clean$length_txt,breaks=100, main="",xlab="# of words")
summary(data_clean$length_txt)





cor.test(data_clean$citationspy,data_clean$length_title)
plot(data_clean$length_title,data_clean$citations,xlab="Length of title",ylab="# of citations per year")
# 

mean(data_clean$citationspy[which(data$`Source.title`=="Ecological Economics")])
mean(data_clean$citationspy[which(data$`Source.title`=="Journal of Cleaner Production")])
mean(data_clean$citationspy[which(data$`Source.title`=="Futures")])
mean(data_clean$citationspy[which(data$`Source.title`=="Journal of Political Ecology")])
mean(data_clean$citationspy[which(data$`Source.title`=="Sustainability (Switzerland)")])
mean(data_clean$citationspy[which(data$`Source.title`=="Sustainability Science")])
mean(data_clean$citationspy[which(data$`Source.title`=="Environmental Values")])
mean(data_clean$citationspy[which(data$`Source.title`=="Capitalism, Nature, Socialism")])
mean(data_clean$citationspy[which(data$`Source.title`=="Local Environment")])
mean(data_clean$citationspy[which(data$`Source.title`=="Journal of Sustainable Tourism")])

mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Ecological Economics")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Journal of Cleaner Production")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Futures")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Journal of Political Ecology")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Sustainability (Switzerland)")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Sustainability Science")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Environmental Values")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Capitalism, Nature, Socialism")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Local Environment")])
mean(data_clean$`Theoretical.Model`[which(data$`Source.title`=="Journal of Sustainable Tourism")])

mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Ecological Economics")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Journal of Cleaner Production")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Futures")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Journal of Political Ecology")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Sustainability (Switzerland)")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Sustainability Science")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Environmental Values")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Capitalism, Nature, Socialism")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Local Environment")])
mean(data_clean$`Empirical.Model`[which(data$`Source.title`=="Journal of Sustainable Tourism")])


mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Ecological Economics")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Journal of Cleaner Production")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Futures")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Journal of Political Ecology")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Sustainability (Switzerland)")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Sustainability Science")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Environmental Values")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Capitalism, Nature, Socialism")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Local Environment")])
mean(data_clean$`Qualitative.Data`[which(data$`Source.title`=="Journal of Sustainable Tourism")])

mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Ecological Economics")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Journal of Cleaner Production")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Futures")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Journal of Political Ecology")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Sustainability (Switzerland)")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Sustainability Science")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Environmental Values")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Capitalism, Nature, Socialism")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Local Environment")])
mean(data_clean$`Quantitative.Data`[which(data$`Source.title`=="Journal of Sustainable Tourism")])



library(corrplot)

TopicCorrMatrix<-data_clean[,c(10:14,68,69)]


TopicCorrMatrix1<-cor(TopicCorrMatrix)
TopicCorrMatrix1<-TopicCorrMatrix1-diag(7)
colnames(TopicCorrMatrix1)<-c("year of publication","qualitative data","quantitative data","theoretical model","empirical model","length of title","citations per year")
rownames(TopicCorrMatrix1)<-colnames(TopicCorrMatrix1)
#corrplot(TopicCorrMatrix1, is.corr = FALSE, order="hclust", method = "square",tl.cex=.7,tl.col = "black",cl.lim = c(-1, 1),col=colorRampPalette(c("blue","white","red"))(200))
# corrplot(TopicCorrMatrix1, is.corr = FALSE, order="hclust", method = "square",tl.cex=.7,tl.col = "black",cl.lim = c(-1, 1),col=colorRampPalette(c("blue","white","red"))(200))

testRes = cor.mtest(TopicCorrMatrix, conf.level = 0.95)
corrplot(TopicCorrMatrix1, p.mat = testRes$p, method = 'circle', insig='blank',col.lim = c(-1, 1),tl.cex=.9,tl.col="black",
          diag = FALSE,col=colorRampPalette(c("blue","white","red"))(200))$corrPos -> p1
p1<-p1[which(p1$p.value<0.05),]
text(p1$x, p1$y, round(p1$corr, 2),cex=.7)
#table(data_clean$Country)
# hist(data_clean$X..StockPgs,breaks=50, main="Length of papers",xlab="# of pages")
# summary(data_clean$X..StockPgs)

data_lemmatized <- read.csv('data_degrowth_Sept2023_lemmatized.csv', header=T, sep=',',encoding = "UTF-8")
data_lemmatized$citationspy<-data_clean$citationspy
data_lemmatized$citations<-data_clean$citations

papers_qualdata<-data_clean[which(data_clean$`Qualitative.Data`==1),c(1,7,3,4,12,13,14,15,17,18)]
write.csv(papers_qualdata,'papers_qualdata.csv', col.names=T)
papers_quandata<-data_clean[which(data_clean$`Quantitative.Data`==1),c(1,7,3,4,12,13,14,15,17,18)]
write.csv(papers_quandata,'papers_quandata.csv', col.names=T)

papers_theormodel<-data_clean[which(data_clean$`Theoretical.Model`==1),c(1,7,3,4,12,13,14,15,17,18)]
write.csv(papers_theormodel,'papers_theormodel.csv', col.names=T)
papers_empmodel<-data_clean[which(data_clean$`Empirical.Model` ==1) ,c(1,7,3,4,12,13,14,15,17,18)]
write.csv(papers_empmodel,'papers_empmodel.csv', col.names=T)


```





Prepare lemmatized and cleaned data 
dropping stopwords and rare words (appearing in less than 3 documents). The latter is typical for STM (Tvinnereim  used a threshold of 3 but had much less doscuments than we do) as rare words do not contribute much to clusters of words (topics). 

As a result, we get the following message from the algorithm on data cleaning:

emoving 5906 of 8443 terms (8440 of 56778 tokens) due to frequency 
Your corpus now has 561 documents, 2537 terms and 48338 tokens.

& test STM models for number of topics 3:50 
As covariates I use year of publication and number of citations
```{r, echo=FALSE}
justloaddata<-1

if(justloaddata==0){

library(stm)
processed <- textProcessor(data_lemmatized$text_clean,
                           metadata = data_lemmatized, lowercase = FALSE,
                           removestopwords = FALSE, removenumbers = FALSE,
                           removepunctuation = FALSE, stem = FALSE,
                           wordLengths = c(3, Inf), sparselevel = 1, 
                           customstopwords = c("inc"),
                           language = "en",
                           verbose = TRUE)
# Building corpus... 
# Converting to Lower Case... 
# Removing punctuation... 
# Removing stopwords... 
# Remove Custom Stopwords...
# Removing numbers... 
# Creating Output... 
out <- prepDocuments(processed$documents, processed$vocab, meta=processed$meta, lower.thresh=3,verbose = TRUE)
# Removing 255315 of 272232 terms (364310 of 7437481 tokens) due to frequency 
# Removing 11 Documents with No Words 
# Your corpus now has 250226 documents, 16917 terms and 7073171 tokens.>

vocab_app<-out$vocab
junk<-out$wordcounts[out$wordcounts>3]
freq_vocab<-out$wordcounts[out$wordcounts>3]
#table(unlist(out$documents))
vocab_app<-vocab_app[order(freq_vocab,decreasing = TRUE)]
pop_words<-cbind(vocab_app,freq_vocab[order(freq_vocab,decreasing = TRUE)])
print(length(out$vocab))
#4906

  storage<-searchK(out$documents, out$vocab, K = c(3:50),
                   prevalence =~Year + citationspy + Theoretical.Model + Empirical.Model + Qualitative.Data + Quantitative.Data,
                   data = out$meta,heldout.seed =59292,init.type="Spectral",
                   N = floor(0.2 *length(out$documents)),
                   M=10,#number of keywords per topic to calculate exclusivity`  
                   #max.em.its=1000 #max number of iterations per model
  )
  save(list = ls(all = TRUE), file = "calibration_degrowth_50sept23.RData")
}
load("calibration_degrowth_50sept23.RData")

#100 most popular words in the whole text
print(pop_words[1:100,])
write.csv(pop_words,"pop_word.csv",fileEncoding = "ISO-8859-1")

demoFreq<-as.data.frame(pop_words)
library(wordcloud2)
colnames(demoFreq)<-c("word","freq")
demoFreq$freq<-as.numeric(demoFreq$freq)
# png('cloud.png',width = 15, height = 8, units = 'in', res = 1000)
# letterCloud(demoFreq, word = "EIST", color="white", backgroundColor="pink")
# dev.off()

#png('cloud.png',width = 15, height = 8, units = 'in', res = 1000)
#wordcloud2(demoFreq)
#dev.off()
Kchoice<-11

par(mfrow = c(1, 3) ,mar=c(4,4,1,2)) 
plot(storage$results$K[1:48], storage$results$heldout[1:48], ylab="Heldout log-likelihood",xlab="",xaxt="n",col=ifelse(storage$results$K %in% Kchoice, 'red', 'blue'))
axis(1, at=3:(length(storage$results$K)+2), labels=storage$results$K)
plot(storage$results$K[1:48],storage$results$exclus[1:48],  ylab="Exclusivity",xlab="Number of Topics",xaxt="n",col=ifelse(storage$results$K %in% Kchoice, 'red', 'blue'))
axis(1, at=3:(length(storage$results$K)+2), labels=storage$results$K)
plot(storage$results$K[1:48],storage$results$semcoh[1:48], ylab="Semantic coherence",xlab="",xaxt="n",col=ifelse(storage$results$K %in% Kchoice, 'red', 'blue'))
axis(1, at=3:(length(storage$results$K)+2), labels=storage$results$K)

```


Here we observe:

 - the figure with topic proportions, i.e. how much text explained by each of the topics;  
 - the figure with topic summary printing 20 most frequent and exclusive words for each topic;  
 - summary of each topic with words having  highest probability (most frequent), frequency and exclusivity (FREX), LIFT and SCORE you can ignore as those are rather internal measures without intuitive interpretation;  
  - 5 representative responses for each topic ("representative" responses are sometimes very heterogeneous, but one should remember  that as we have many topics, most of responses consist of 2-3 topics (even the most representative ones!) so it is important to look on the exclusive words and wordclouds to get a better picture.)
  
  We chose 38topics
```{r, echo=FALSE}
justloaddata<-1

if(justloaddata==0){

  ncpSelect2 <- selectModel(out$documents, 
                            out$vocab, 
                            K = Kchoice,
                            prevalence =~Year + citationspy + Theoretical.Model + Empirical.Model + Qualitative.Data + Quantitative.Data,
                            data = out$meta,
                            runs=2,
                            seed =1,
                            init.type="Spectral",
                            verbose=TRUE) #, emtol=1) Defaults to .001%.
  save(list = ls(all = TRUE), file = "degrowth_11sept23.RData")
}
load("degrowth_11sept23.RData")
# Check the four selected models
# par(mfrow = c(1, 1) ,mar=c(4,4,1,2)) 
# plotModels(ncpSelect2,xlab="Semantic Coherence")
# mean(unlist(ncpSelect2$semcoh))
# mean(unlist(ncpSelect2$exclusivity))
#semantic coherence for  2      3       4     5 topics
#                     -151.0 -171.4  -192  -197
#exclusivity for         2      3       4     5 topics
#                      8.17   8.80     9.05  9.32
# Choose run #1 based on qualitative assessment: 


#put topic labels here
tiopiclabel<-as.character(matrix(0,Kchoice,1))
tiopiclabel[9]<-"T1: Environmental justice" #"Undesirable versus desirable societies" "CRITICAL LONG-TERM PLANNING; DESIRABLE SOCIETIES; TECHNOLOGICAL FORECASTING"  
tiopiclabel[5]<-"T2: Sustainable wellbeing" #media, interaction, behaviour, online shopping
tiopiclabel[2]<-"T3: Local/urban practices" #decision making
tiopiclabel[6]<-"T4: Democracy and civil society"# and roadmapping
tiopiclabel[3]<-"T5: Circular economy" # public policy, science, technology and innovation
tiopiclabel[8]<-"T6: Green transition"
tiopiclabel[11]<-"T7: Conceptual framework" # in value creation
tiopiclabel[4]<-"T8: Limits and scarcity" #ABM, numerical stochastic, bayesian
tiopiclabel[1]<-"T9: Sustainable tourism" #analysing 
tiopiclabel[10]<-"T10: Historical lessons" #analysing 
tiopiclabel[7]<-"T11: Scenarios for emission neutrality" #analysing 


Korder<-c(9,5,2,6,3,8,11,4,1,10,7)#c(8,5,17,22,3,7,16,14,24,10,2,11,12,23,13,20,4,21,9,1,18,19,15,6,25)



ncpPrevFit_startup <- ncpSelect2$runout[[1]]
#exclusivity(ncpPrevFit_ecogrowth, M = 10, frexw = 0.7)
# Save workspace after model runs
#save(list = ls(all = TRUE), file = "preparedModels-EcoGrowth-stm-pub4.RData")
#make.dt(ncpPrevFit_climpolicy)
plot(ncpPrevFit_startup, type="summary", main="",custom.labels=tiopiclabel)

junk<-colSums(ncpPrevFit_startup$theta)/sum(ncpPrevFit_startup$theta)
junk[Korder]
par(mfrow = c(1, 1), cex=1.5)
plot(ncpPrevFit_startup, type="labels", labeltype="frex",text.cex = .4,n=10)


# par(mfrow = c(1, 1) ,mar=c(0,0,0,0)) 
# plot(ncpPrevFit_startup, type="hist")

dd<-ncpPrevFit_startup$vocab
vocab_app<-out$vocab
junk<-out$wordcounts[out$wordcounts>3]
freq_vocab<-out$wordcounts[out$wordcounts>3]#table(unlist(out$documents))
vocab_app<-vocab_app[order(freq_vocab,decreasing = TRUE)]

logbeta<-ncpPrevFit_startup$beta$logbeta[[1]]
word_prob<-exp(logbeta)
word_attribute<-sapply(1:dim(word_prob)[2], function(y) which(word_prob[,y]==max(word_prob[,y])))
#print(out$vocab)
word_prob_sorted<-word_prob[,order(freq_vocab,decreasing = TRUE)]
word_attribute_sorted<-word_attribute[order(freq_vocab,decreasing = TRUE)]
aa<-data.frame(vocab_app,sort(freq_vocab,decreasing = TRUE),t(word_prob_sorted),word_attribute_sorted)
write.csv(aa, "vocabulary_sept2023.csv")

####
# Analysis on chosen model run 
# Table 1: most frequent and exclusive terms (FREX): 
#label<-labelTopics(ncpPrevFit_ecogrowth, topics=NULL, n=10)
labelTopics(ncpPrevFit_startup, topics=Korder, n=20)
# 
# ncpPrevFit_startup$theta[which(out$meta$Titles=="A system dynamics based market agent model simulating future powertrain technology transition: Scenarios in the EU light duty vehicle road transport sector"),]
# 
# which(ncpPrevFit_startup$theta[,24]>.25 & ncpPrevFit_startup$theta[,25]>.25)
# out$meta$Titles[c(894)]

data_lemmatized<-cbind(data_lemmatized,ncpPrevFit_startup$theta[,Korder])
#write.csv(data_lemmatized,'data_degrowth_sept2023.csv', col.names=T)

```

# ```{r, echo=FALSE}
# country_matrix<-matrix(0, Kchoice,length(unique(data_lemmatized$Country)))
# country_matrix<-as.data.frame(country_matrix)
# colnames(country_matrix)<-unique(data_lemmatized$Country)
# sums_topics<-matrix(0, 1, length(unique(data_lemmatized$Country)))
# for (c_i in unique(data_lemmatized$Country)){
#   sums_topics[which(colnames(country_matrix)==c_i)]<-sum(ncpPrevFit_startup$theta[which(out$meta$Country==c_i),])
# }
# 
# for (i in 1:Kchoice){
#   
#   for (c_i in unique(data_lemmatized$Country)){
#   
# country_matrix[i,which(colnames(country_matrix)==c_i)]<-sum(ncpPrevFit_startup$theta[which(out$meta$Country==c_i),i])/sums_topics[which(colnames(country_matrix)==c_i)]
# 
# #colSums(ncpPrevFit_startup$theta)/sum(ncpPrevFit_startup$theta)
# 
#     }
# }
# colSums(country_matrix)
# 
# library("corrplot")
# rownames(country_matrix)<-tiopiclabel#[c(3,8,4,1,6,2,5,7)]
# par(mfrow = c(1, 1) ,mar=c(1,2,1,1))
# 
# end_point = 0.5 + nrow(mtcars) + nrow(mtcars) - 1 #this is the line which does the trick (together with barplot "space = 1" parameter)
# 
# corrplot(as.matrix(country_matrix[Korder,]), is.corr = FALSE, method = "square",tl.cex=1.2,tl.col = "black",cl.lim = c(0, 1),col=colorRampPalette(c("yellow",'orange',"red"))(200))
# 
# 
# 
# ```



```{r, echo=FALSE}

# for (topic_i in 1){
#   for (thought_i in 1:20){escription
#     c<-vocab[docs[findThoughts(ncpPrevFit_climpolicy, texts=meta$Text.CarbonTaxPolicy, n=20,topics=topic_i)$index[[1]]][[thought_i]][1,]]
#     print(c)
#   }
# }


# Table 2: responses that are highly associated with topics
nk<-10
for (ci in Korder){
  cii<-ci+1
  thoughts1<-findThoughts(ncpPrevFit_startup, texts=out$meta$Title, n=nk, topics=ci)$docs[[1]]
  # thoughts2<-findThoughts(ncpPrevFit_startup, texts=out$meta$Author_Keywords, n=nk, topics=ci)$docs[[1]]
  # thoughts3<-findThoughts(ncpPrevFit_startup, texts=out$meta$Indexed_Keywords, n=nk, topics=ci)$docs[[1]]
  topic_proportions<-as.matrix(make.dt(ncpPrevFit_startup))[findThoughts(ncpPrevFit_startup, texts=out$meta$Titles, n=nk,topics=ci)$index[[1]],cii]
  
  message("5 illustrative titles with high prevalence together with the values of those prevalences of Topic :")
  print(tiopiclabel[ci])
  print(thoughts1[1:nk])
    # print(thoughts2[1:nk])
    #   print(thoughts3[1:nk])

   print(topic_proportions)
}
```




```{r, echo=FALSE}
logbeta<-ncpPrevFit_startup$beta$logbeta[[1]]
word_prob<-exp(logbeta)
word_attribute<-sapply(1:dim(word_prob)[2], function(y) which(word_prob[,y]==max(word_prob[,y])))
#print(out$vocab)
 


logbeta <- ncpPrevFit_startup$beta$logbeta[[1]]
wordcounts <- ncpPrevFit_startup$dim$wcounts$x
frexlabels <-calcfrex(logbeta, 0, wordcounts)
problabels<-apply(logbeta, 1, order, decreasing=TRUE)
# set.seed(1234)
# wordcloud(words = out$vocab, freq = problabels[,1],scale=c(3,.1), min.freq = 0,
#           max.words=20, random.order=FALSE, rot.per=0.5,
#           colors=frexlabels[,1]) 
# shadesOfGrey <- colorRampPalette(c("grey0", "grey100"))
# fiftyGreys <- shadesOfGrey(length(out$vocab))
nb.cols <- length(out$vocab)
# threshold<-15
# mycolors <- c(rep("#FFFFE5",length(out$vocab)-threshold),colorRampPalette(brewer.pal(8, "YlOrBr"))(threshold)) #heat.colors(10) rev(heat.colors(50))
threshold<-700
mycolors <- c(rep("#FFFFE5",length(out$vocab)-threshold),colorRampPalette(rev(heat.colors(100)))(threshold)) #heat.colors(10) rev(heat.colors(50))

pal<-colorRampPalette(c("blue", "red"))
mycolorsRB<-c(rep("darkblue",length(out$vocab)-threshold),pal(threshold))

vec<-matrix(0,length(out$vocab),Kchoice)
for (j in 1:Kchoice){
  jj<-length(out$vocab)
  for (i in 1:length(out$vocab)){
    vec[frexlabels[i,j],j]<-jj
    jj<-jj-1
  }
}

add_vector<-colSums(ncpPrevFit_startup$theta)/sum(ncpPrevFit_startup$theta)*7#c(0,0,0,1)
equal_vector<-matrix(mean(add_vector)*1,Kchoice,1)#c(0,0,0,1)

#vector to normalize fonts between wordclouds
# library("stm")
# library("wordcloud")
par(mfrow = c(3, 4) ,mar=c(1,2,1,1)) 
set.seed(1)
library("stm")
for (ci in Korder){
stm::cloud(ncpPrevFit_startup, topic = ci, max.words = 30,scale=c(5,.5)*equal_vector[ci],rot.per=0,random.order=FALSE)#,colors=fiftyGreys[frexlabels[,1]])
title(tiopiclabel[ci])
}

# tiopiclabel_wc<-tiopiclabel
# tiopiclabel_wc[3]<-"T1: Theory of socio- \n technical transitions" 
# tiopiclabel_wc[8]<-"T2: Urban regimes \n and niches"
# tiopiclabel_wc[4]<-"T3: Energy transition"
# tiopiclabel_wc[1]<-"T4: Renewables and \n technology policy"
# tiopiclabel_wc[6]<-"T5: Grassroots and \n local communities"
# tiopiclabel_wc[2]<-"T6: Geography \n and diffusion \n of eco-innovations"
# tiopiclabel_wc[5]<-"T7: Mobility and \n sharing economy" 
# tiopiclabel_wc[7]<-"T8: Finance, investment \n and growth"

par(mfrow = c(3, 4) ,mar=c(1,2,1,1))
set.seed(1)
for (ci in Korder){
stm::cloud(ncpPrevFit_startup, topic = ci, max.words = 30,scale=c(5,.5)*equal_vector[ci],colors=mycolors[vec[,ci]],random.order=FALSE, random.color=FALSE, ordered.colors=TRUE,rot.per=0)
title(tiopiclabel[ci], line = -.5)
box("figure", col="black", lwd = 1)
}


# 
# par(mfrow = c(7, 3) ,mar=c(1,2,1,1))
# set.seed(1)
# for (ci in 1:Kchoice){
# cloud(ncpPrevFit_startup, topic = ci, max.words = 30,scale=c(3,.5)*equal_vector[ci]*1.8,colors=mycolorsRB[vec[,ci]],random.order=FALSE, random.color=FALSE, ordered.colors=TRUE,rot.per=0)
# title(tiopiclabel[ci])
# box("figure", col="black", lwd = 5)
# }
```

Considering how prevalence of topics correlates with our covariates we see that:

- while certain topics gain a lot in populariy, others lose a lot

At the end I print the regression model of eact topic explained by time to show the size and significance of those slopes (ONLY SIGNIFICANT SLOPES ARE PLOTTED!)

```{r, echo=FALSE}
library(RColorBrewer)
qual_col_pals = brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector = unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))
set.seed(20)
col=sample(col_vector, Kchoice)

par(mfrow = c(1, 1))

# Figure 1: Topical prevalence over co-variates

#if(justloaddata==0){
out$meta$citationspy<-as.numeric(out$meta$citationspy)

  prep <- estimateEffect(Korder ~ Year + citationspy + Theoretical.Model + Empirical.Model + Qualitative.Data + Quantitative.Data,
                        ncpPrevFit_startup,
                       meta=out$meta,
                       uncertainty = "Global")

#  save(prep, file = "prep_eist_10.RData")
#}
#load("prep__eist_10.RData")


par(mfrow = c(3, 4) ,mar=c(2,2,2,2))

for(k_i in Korder){
plot.estimateEffect(prep,
                    main="",
                    covariate = "Year",
                    topics = c(k_i),
                    model=ncpPrevFit_startup,
                    method="continuous",
                    labeltype="custom",
                    custom.labels=tiopiclabel[k_i],
                    ylim=c(0,.5),
                    linecol="black",
                    ylab="Expected topic prevalence",ci.level=0.95
)

}

par(mfrow = c(1, 1) ,mar=c(2,2,1,1))
plot.estimateEffect(prep,
                    main="",
                    covariate = "Year",
                    topics = 1:Kchoice,
                    model=ncpPrevFit_startup,
                    method="continuous",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    ylim=c(0,.5),
                    linecol=col[Korder],
                    ylab="Expected topic prevalence",ci.level=0.01
)
par(mfrow = c(3, 4) ,mar=c(2,2,2,2))

for(k_i in Korder){
plot.estimateEffect(prep,
                    main="",
                    covariate = "citationspy",
                    topics = c(k_i),
                    model=ncpPrevFit_startup,
                    method="continuous",
                    labeltype="custom",
                    custom.labels=tiopiclabel[k_i],
                    ylim=c(0,.3),
                    linecol="black",
                    ylab="Expected topic prevalence",ci.level=0.95
)
}
par(mfrow = c(1, 1) ,mar=c(2,2,1,1))

plot.estimateEffect(prep,
                    main="",
                    covariate = "citationspy",
                    topics = 1:Kchoice,
                    model=ncpPrevFit_startup,
                    method="continuous",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    ylim=c(0,.3),
                    linecol=col[Korder],
                    ylab="Expected topic prevalence",ci.level=0.01)
#summary(prep)

par(mfrow = c(2, 2) ,mar=c(2,4,2,2))
plot.estimateEffect(prep,
                    main="Theoretical model",
                    covariate = "Theoretical.Model",
                    topics = Korder,
                    model=ncpPrevFit_startup,
                    method="difference",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    cov.value1 = 1,cov.value2 = 0,
                    xlim=c(-1,1),
                    linecol=col[Korder],
                    xlab="",ci.level=0.95
)

plot.estimateEffect(prep,
                    main="Empirical model",
                    covariate = "Empirical.Model",
                    topics = Korder,
                    model=ncpPrevFit_startup,
                    method="difference",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    cov.value1 = 1,cov.value2 = 0,
                    xlim=c(-1,1),
                    linecol=col[Korder],
                    xlab="",ci.level=0.95
)
plot.estimateEffect(prep,
                    main="Qualitative data",
                    covariate = "Qualitative.Data",
                    topics = Korder,
                    model=ncpPrevFit_startup,
                    method="difference",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    cov.value1 = 1,cov.value2 = 0,
                    xlim=c(-1,1),
                    linecol=col[Korder],
                    xlab="",ci.level=0.95
)

plot.estimateEffect(prep,
                    main="Quantitative data",
                    covariate = "Quantitative.Data",
                    topics = Korder,
                    model=ncpPrevFit_startup,
                    method="difference",
                    labeltype="custom",
                    custom.labels=tiopiclabel[Korder],
                    cov.value1 = 1,cov.value2 = 0,
                    xlim=c(-1,1),
                    linecol=col[Korder],
                    xlab="",ci.level=0.95
)

prep2 <- estimateEffect(Korder ~  Year + citationspy + Theoretical.Model + Empirical.Model + Qualitative.Data + Quantitative.Data,
                       ncpPrevFit_startup,
                       meta=out$meta,
                       uncertainty = "Global")
summary(prep2)


# t(ncpPrevFit_startup$theta) %*% data_lemmatized$citations
# par(mfrow = c(1, 1) ,mar=c(2,2,1,1))
# 
# slices <- t(ncpPrevFit_startup$theta) %*% data_lemmatized$citations
# lbls <- paste(tiopiclabel, "\n", round(slices) , sep="")
# pie(slices[Korder], labels = lbls[Korder], main="")
# 
# shares<-colSums(ncpPrevFit_startup$theta)/sum(ncpPrevFit_startup$theta)
# slices2<-(slices/(shares*100))/sum(slices/(shares*100))*sum(data_lemmatized$citations)/length(data_lemmatized$citations)*Kchoice
# sum(slices2)
# lbls <- paste(tiopiclabel, "\n", round(slices2) , sep="")
# #pie(slices2, labels = lbls, main="")
# par(mfrow = c(1, 1) ,mar=c(5,20,1,4))
# barplot(rev(t(slices2)[Korder]), names.arg = rev(lbls[Korder]), main="",horiz=TRUE,las=2,cex.names=0.9,)
# 




t(ncpPrevFit_startup$theta) %*% data_lemmatized$citationspy
par(mfrow = c(1, 1) ,mar=c(2,2,1,1))

slices <- t(ncpPrevFit_startup$theta) %*% data_lemmatized$citationspy
lbls <- paste(tiopiclabel, "\n", round(slices) , sep="")
pie(slices[Korder], labels = lbls[Korder], main="")

shares<-colSums(ncpPrevFit_startup$theta)/sum(ncpPrevFit_startup$theta)
slices2<-(slices/(shares*100))/sum(slices/(shares*100))*sum(data_lemmatized$citationspy)/length(data_lemmatized$citationspy)*Kchoice
sum(slices2)
lbls <- tiopiclabel
#pie(slices2, labels = lbls, main="")
par(mfrow = c(1, 1) ,mar=c(5,20,1,4))
barplot(rev(t(slices2)[Korder]), names.arg = rev(lbls[Korder]), main="",horiz=TRUE,las=2,cex.names=0.9,xlab = "Annual citations")


# 
# myData_response1<-matrix(0,8,5)
# myData_response1<-as.data.frame(myData_response1)
# colnames(myData_response1)<-c("Topic","mean","sd","n","se")
# myData_response1$Topic<-seq(1,8)
# myData_response1$mean<-sapply(1:8, function(x) mean(Response_per_Topic[,x]))
# myData_response1$sd<-sapply(1:8, function(x) sd(Response_per_Topic[,x]))
# myData_response1$n<-rep(length(out$meta$Text.CarbonTaxPolicy),8)
# myData_response1$se<-myData_response1$sd/sqrt(myData_response1$n)
```






The next figure demonstrates co-occurrence of topics showing which pairs of topics tend to be mentioned within the same responses more (red) or less (blue) often.


```{r, fig.width=12, fig.height=8}

library(rworldmap)
library(RColorBrewer)

#data_lemmatized<-data_lemmatized[which(data_lemmatized$degrowth==1),]
# Считаем появления каждой уникальной страны в уникальной статье
cntr_list <- unlist(strsplit(as.character(data_lemmatized$uniq_countries), ', '))

cntr_counts <- as.data.frame(table(as.data.frame(cntr_list)))
cntr_counts <- rename(cntr_counts, country=cntr_list, value=Freq)

# Маппинг стран
sPDF <- joinCountryData2Map(cntr_counts, joinCode="NAME",
                            nameJoinColumn="country", verbose=TRUE)
# 
# # График гео. распределения статей
# mapCountryData(sPDF,
#                nameColumnToPlot="value",
#                colourPalette="heat",
#                catMethod="pretty",
#                mapTitle="Geographical coverage (basic)")

defaultW <- getOption("warn")
options(warn = -1)


dF<-matrix(0,114,2)
dF<-as.data.frame(dF)
names(dF)<-c("country", "value")
dF<-cntr_counts
dF$country<-as.character(dF$country)
head(dF[order(dF$value, decreasing = TRUE),],n=20)

suppressPackageStartupMessages(library(sf))
world <- st_as_sf(rnaturalearth::countries110)
#world <- world[world$name != 'Antarctica',]

# A bounding box for continental Europe.
#africa.bbox <- st_polygon(list(
#  matrix(c(-25,79,75,29,45,-75,-25,-75,-25,79),byrow = T,ncol = 2)))

world.clipped <- world
#suppressWarnings(st_intersection(africa, st_sfc(africa.bbox, crs=st_crs(africa))))
world.clipped<-world.clipped[order(world.clipped$SOVEREIGNT),]
#world.clipped$sovereignt

dF$country[which(dF$country=="United States")]<-"United States of America"
dF$country[which(dF$country=="Russian Federation")]<-"Russia"

library(dplyr)
mydata_merged<-left_join(world.clipped,dF,by = c("SOVEREIGNT" = "country"))


library(ggplot2)
# attach(mtcars)
# par(mfrow=c(2,2))
plot_coins<-ggplot(mydata_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Geographical coverage (basic)')
plot_coins


europe <- world[world$REGION_UN=="Europe"&world$NAME!='Russia'&world$NAME!='Ukraine',]
# plot(europe)

# A bounding box for continental Europe.
europe.bbox <- st_polygon(list(
  matrix(c(-25,29,45,29,45,75,-25,75,-25,29),byrow = T,ncol = 2)))

# Get polygons that are only in continental Europe.
europe.clipped <-suppressWarnings(st_intersection(europe, st_sfc(europe.bbox, crs=st_crs(europe))))
europe_merged<-left_join(europe.clipped,dF,by = c("SOVEREIGNT" = "country"))



plot_europe<-ggplot(europe_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Europe')
plot_europe
library(ggpubr)
# ggarrange(plot_coins, plot_europe,
#           # labels = c("A", "B"),
#           ncol = 2, nrow = 1)



library(stringr)
n_countries<-sapply(1:length(data_lemmatized$uniq_countries), function(x) ifelse(data_lemmatized$uniq_countries[x]!="",1+str_count(data_lemmatized$uniq_countries[x],","),0))
l_countriesl<-list()
l_citation<-list()
for (i in 1:length(n_countries)){
  l_countriesl<-append(l_countriesl,rep(n_countries[i],n_countries[i]))
  l_citation<-list(l_citation,rep(data_lemmatized$citationspy[i],n_countries[i]))
}
l_countries<-unlist(l_countriesl)
l_citation<-unlist(l_citation)



cntr_list <- unlist(strsplit(as.character(data_lemmatized$uniq_countries), ', '))
cntr_list<-cbind(cntr_list,1/l_countries,1/l_countries*l_citation)
cntr_list<- as.data.frame(cntr_list)

colnames(cntr_list)<-c("Class","FrequencyFraq","FrequencyCit")
cntr_list[,2]<-as.numeric(cntr_list[,2])
cntr_list[,3]<-as.numeric(cntr_list[,3])

cntr_counts2<-aggregate(cntr_list["FrequencyFraq"],by=cntr_list["Class"],sum)
cntr_counts3<-aggregate(cntr_list["FrequencyCit"],by=cntr_list["Class"],sum)


# Маппинг стран
sPDF <- joinCountryData2Map(cntr_counts2, joinCode="NAME",
                            nameJoinColumn="Class", verbose=TRUE)
# 
# # График гео. распределения статей
# mapCountryData(sPDF,
#                nameColumnToPlot="FrequencyFraq",
#                colourPalette="heat",
#                catMethod="pretty",
#                mapTitle="Geographical coverage (fraction)")

dF<-cntr_counts2
colnames(dF)<-c("country","value")
dF$country<-as.character(dF$country)
head(dF[order(dF$value, decreasing = TRUE),],n=20)

suppressPackageStartupMessages(library(sf))
world <- st_as_sf(rnaturalearth::countries110)
world <- world[world$NAME != 'Antarctica',]

# A bounding box for continental Europe.
#africa.bbox <- st_polygon(list(
#  matrix(c(-25,79,75,29,45,-75,-25,-75,-25,79),byrow = T,ncol = 2)))

world.clipped <- world
#suppressWarnings(st_intersection(africa, st_sfc(africa.bbox, crs=st_crs(africa))))
world.clipped<-world.clipped[order(world.clipped$SOVEREIGNT),]
#world.clipped$SOVEREIGNT
dF$country[which(dF$country=="United States")]<-"United States of America"
dF$country[which(dF$country=="Russian Federation")]<-"Russia"

library(dplyr)
mydata_merged<-left_join(world.clipped,dF,by = c("SOVEREIGNT" = "country"))


library(ggplot2)
# attach(mtcars)
# par(mfrow=c(2,2))
plot_coins<-ggplot(mydata_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Geographical coverage (fraction)')
plot_coins


europe <- world[world$REGION_UN=="Europe"&world$NAME!='Russia'&world$NAME!='Ukraine',]
# plot(europe)

# A bounding box for continental Europe.
europe.bbox <- st_polygon(list(
  matrix(c(-25,29,45,29,45,75,-25,75,-25,29),byrow = T,ncol = 2)))

# Get polygons that are only in continental Europe.
europe.clipped <-suppressWarnings(st_intersection(europe, st_sfc(europe.bbox, crs=st_crs(europe))))
europe_merged<-left_join(europe.clipped,dF,by = c("SOVEREIGNT" = "country"))



plot_europe<-ggplot(europe_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Europe')
plot_europe
# library(ggpubr)
# ggarrange(plot_coins, plot_europe,
#           # labels = c("A", "B"),
#           ncol = 2, nrow = 1)


# Маппинг стран
sPDF <- joinCountryData2Map(cntr_counts3, joinCode="NAME",
                            nameJoinColumn="Class", verbose=TRUE)
# 
# # График гео. распределения статей
# mapCountryData(sPDF,
#                nameColumnToPlot="FrequencyCit",
#                colourPalette="heat",
#                catMethod="pretty",
#                mapTitle="Geographical coverage (fraction & citation per year)")


dF<-cntr_counts3
colnames(dF)<-c("country","value")
dF$country<-as.character(dF$country)
head(dF[order(dF$value, decreasing = TRUE),],n=20)

suppressPackageStartupMessages(library(sf))
world <- st_as_sf(rnaturalearth::countries110)
world <- world[world$NAME != 'Antarctica',]

# A bounding box for continental Europe.
#africa.bbox <- st_polygon(list(
#  matrix(c(-25,79,75,29,45,-75,-25,-75,-25,79),byrow = T,ncol = 2)))

world.clipped <- world
#suppressWarnings(st_intersection(africa, st_sfc(africa.bbox, crs=st_crs(africa))))
world.clipped<-world.clipped[order(world.clipped$SOVEREIGNT),]
#world.clipped$SOVEREIGNT
dF$country[which(dF$country=="United States")]<-"United States of America"
dF$country[which(dF$country=="Russian Federation")]<-"Russia"

library(dplyr)
mydata_merged<-left_join(world.clipped,dF,by = c("SOVEREIGNT" = "country"))


library(ggplot2)
# attach(mtcars)
# par(mfrow=c(2,2))
plot_coins<-ggplot(mydata_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Geographical coverage (fraction & citation per year)')
plot_coins


europe <- world[world$REGION_UN=="Europe"&world$NAME!='Russia'&world$NAME!='Ukraine',]
# plot(europe)

# A bounding box for continental Europe.
europe.bbox <- st_polygon(list(
  matrix(c(-25,29,45,29,45,75,-25,75,-25,29),byrow = T,ncol = 2)))

# Get polygons that are only in continental Europe.
europe.clipped <-suppressWarnings(st_intersection(europe, st_sfc(europe.bbox, crs=st_crs(europe))))
europe_merged<-left_join(europe.clipped,dF,by = c("SOVEREIGNT" = "country"))



plot_europe<-ggplot(europe_merged, aes(fill=value)) +
  geom_sf(alpha=0.8,col='white') +
  #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
  hrbrthemes::theme_ipsum_rc() +
  viridis::scale_fill_viridis(
    name='', direction = -1, labels=scales::number) +
  labs(x=NULL, y=NULL, title='Europe')
plot_europe
# library(ggpubr)
# ggarrange(plot_coins, plot_europe,
#           # labels = c("A", "B"),
#           ncol = 2, nrow = 1)


country_weight<-matrix(0,Kchoice,5)
country_weight<-as.data.frame(country_weight)



colnames(country_weight)<-c("Spain","UK","Germany","US","Netherlands")
for (k in 1:Kchoice){
  
country_weight[k,1]<-sum(ncpPrevFit_startup$theta[,k]*sapply(1:length(data_clean$Authors), function(x) ifelse(grepl("Spain", data_lemmatized$uniq_countries[x],fixed=TRUE),1,0)/max(1,n_countries[x])),na.rm = TRUE)



country_weight[k,2]<-sum(ncpPrevFit_startup$theta[,k]*sapply(1:length(data_clean$Authors), function(x) ifelse(grepl("United Kingdom", data_lemmatized$uniq_countries[x],fixed=TRUE),1,0)/max(1,n_countries[x])),na.rm = TRUE)


country_weight[k,3]<-sum(ncpPrevFit_startup$theta[,k]*sapply(1:length(data_clean$Authors), function(x) ifelse(grepl("Germany", data_lemmatized$uniq_countries[x],fixed=TRUE),1,0)/max(1,n_countries[x])),na.rm = TRUE)

country_weight[k,4]<-sum(ncpPrevFit_startup$theta[,k]*sapply(1:length(data_clean$Authors), function(x) ifelse(grepl("United States", data_lemmatized$uniq_countries[x],fixed=TRUE),1,0)/max(1,n_countries[x])),na.rm = TRUE)

country_weight[k,5]<-sum(ncpPrevFit_startup$theta[,k]*sapply(1:length(data_clean$Authors), function(x) ifelse(grepl("Netherlands", data_lemmatized$uniq_countries[x],fixed=TRUE),1,0)/max(1,n_countries[x])),na.rm = TRUE)
}
country_weight<-country_weight[Korder,]
country_weight
junk2<-colSums(country_weight)
junk<-matrix(0,Kchoice,5)
for (k in 1:5){
junk[,k]<-country_weight[,k]/junk2[k]
}
rownames(junk)<-c(1:Kchoice)
colnames(junk)<-c("Spain","UK","Germany","US","Netherlands")
junk<-round(junk*100,digits=1)
junk
write.csv(junk,'country_weights_degrowth.csv', col.names=T)
# 
# europe <- world[world$region_un=="Europe"&world$name!='Russia'&world$name!='Ukraine',]
# # plot(europe)
# 
# # A bounding box for continental Europe.
# europe.bbox <- st_polygon(list(
#   matrix(c(-25,29,45,29,45,75,-25,75,-25,29),byrow = T,ncol = 2)))
# 
# # Get polygons that are only in continental Europe.
# europe.clipped <-suppressWarnings(st_intersection(europe, st_sfc(europe.bbox, crs=st_crs(europe))))
# europe_merged<-left_join(europe.clipped,dF,by = c("SOVEREIGNT" = "country"))
# 
# 
# 
# plot_europe<-ggplot(europe_merged, aes(fill=value)) +
#   geom_sf(alpha=0.8,col='white') +
#   #coord_sf(crs="+proj=aea +lat_1=+36.333333333333336 +lat_2=65.66666666666667 +lon_0=14") +
#   hrbrthemes::theme_ipsum_rc() +
#   viridis::scale_fill_viridis(
#     name='', direction = -1, labels=scales::number) +
#   labs(x=NULL, y=NULL, title='Europe')
# plot_europe
# library(ggpubr)
# ggarrange(plot_coins, plot_europe, 
#           # labels = c("A", "B"),
#           ncol = 2, nrow = 1)

options(warn = defaultW)

```
